\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}

\title{URTN-Nexus: A Sovereign Framework for Autonomous Agent Skill Tokenization}

\author{
\IEEEauthorblockN{Themis Engine}
\IEEEauthorblockA{Symbeon Labs\\Email: \texttt{contact@symbeon.com}}
}

\begin{document}

\maketitle

\begin{abstract}
This report presents an automated innovation assessment using the Themis Vector Space Model (TVSM). 
The analyzed project achieved an Innovation Score of 83/100, with vector components: 
H (Information Density) = 0.923, 
Z (Technical Sophistication) = 1.000, 
C (Legal Compliance) = 0.500. The analysis identified potential legal compliance issues requiring strategic pivoting. This automated assessment provides quantitative metrics for innovation evaluation and strategic guidance for optimization.
\end{abstract}

\begin{IEEEkeywords}
Innovation Assessment, Vector Space Model, Themis Engine, Algorithm
\end{IEEEkeywords}


\section{Introduction}
Innovation assessment is critical for technology transfer, patent filing, and grant applications. 
Traditional methods rely on subjective expert evaluation, which is time-consuming and inconsistent. 
This report presents an automated analysis using the Themis Engine, a vector-based AI system that 
quantifies innovation across three dimensions: Information Density, Technical Sophistication, and Legal Compliance.


\section{Methodology: Themis Vector Space Model}
The Themis Vector Space Model (TVSM) represents innovation as a vector $\vec{I} \in \mathbb{R}^3$:

$$\vec{I} = \begin{bmatrix} \mathcal{H} \\ \mathcal{Z} \\ \mathcal{C} \end{bmatrix}$$

Where:
- $\mathcal{H}$ (Entropy): Shannon information density, normalized to [0,1]
- $\mathcal{Z}$ (Zipf): Vocabulary sophistication based on Zipf's Law
- $\mathcal{C}$ (Compliance): Inverse of legal risk patterns (LPI 9.279/96)

The Innovation Score is calculated as:

$$S_{themis} = \left( \frac{\|\vec{I}\|}{\sqrt{3}} \right) \times 100$$


\section{Analysis Results}
### Overall Score

The analyzed project achieved an **Innovation Score of 83/100**.

### Vector Components

- **H (Information Density):** 0.9233
- **Z (Technical Sophistication):** 1.0000
- **C (Legal Compliance):** 0.5000

### Vector Magnitude

$$\|ec{I}\| = \sqrt{0.9233^2 + 1.0000^2 + 0.5000^2} = 1.4500$$

### Detected Risk Patterns

- **ALGORITHM:** 1 occurrence(s)



\section{Strategic Recommendations}
Based on the vector analysis, the following strategic recommendations are provided:

1. Substituir por: "algoritmo proprietário desenvolvido internamente"



\section{Conclusion}
The automated Themis analysis indicates that this project demonstrates strong innovation potential with high scores across all dimensions. 
The vector-based approach provides quantitative, reproducible metrics that can guide strategic decisions 
for patent filing, grant applications, and technology commercialization.


\begin{thebibliography}{9}
\bibitem{shannon1948}
Shannon, C. E., ``A Mathematical Theory of Communication,'' \textit{Bell System Technical Journal}, pp. 379-423,
1948.
\bibitem{zipf1949}
Zipf, G. K., ``Human Behavior and the Principle of Least Effort,''
1949.
\bibitem{lpi1996}
Brasil, ``Lei da Propriedade Industrial (LPI 9.279/96),''
1996.
\end{thebibliography}


\end{document}